% vim: tw=0:wrap:linebreak
\documentclass[DM,toc,lsstdraft]{lsstdoc}

\usepackage{comment}
\usepackage{datetime}
\usepackage{microtype}

\newcommand{\microarcsec}{$\mu$as\xspace}
\interfootnotelinepenalty=10000


\setcounter{secnumdepth}{3}

%%%%%%%%%%%%%%%%%%%%%
% Introduce mechanism to turn on and off various annotations (\XXX command,
% \begin{notes}, and anything else bracketed by \ifannotated ... \fi)
%
\newif\ifannotated
\annotatedtrue
\annotatedfalse	% uncomment this to hide all annotations (comments, notes, etc)

\ifannotated
	% leave things as-is
\else
	% hide all \XXX commands
	\renewcommand{\XXX}{}

	% hide all \begin{note}...\end{note} text
	\renewenvironment{note}[1][Note]
	{}
	{}
\fi
%%%%%%%%%%%%%%%%%%%%%

\title{Plans and Policies for LSST Alert Distribution}
\author{
    E.C.~Bellm and coauthors
     \emph{for the LSST Project}
}

\setDocRef{LDM-612}
\setDocCurator{E.C.~Bellm}
\date{\today}

\setDocAbstract{%
A major product of the nightly processing of LSST images is a world-public stream of alerts from transient, variable, and moving sources.
Science users will access these alerts through community brokers or through a simple filtering service provided by LSST.
This document provides a guide to the planned alert distribution system to aid science users, broker developers, funding agencies, and LSST Project personnel.
It describes the components of the alert distribution system and the data rights required to access specific scientific products.
It provides guidelines for organizations developing community brokers.
And it describes the planned capabilities of the LSST simple alert filtering service and Science Platform to aid science users in planning for LSST science.
}

%
%   Revision history
%
% OLDEST FIRST: VERSION, DATE, DESCRIPTION, OWNER NAME
\setDocChangeRecord{%
\addtohist{1}{2017-12-28}{Initial version}{Eric Bellm}
}


\begin{document}

\maketitle

\include{sections/introduction}

\include{sections/components}

\include{sections/data_rights}

\include{sections/community_brokers}

\include{sections/mini_broker}

\section{Glossary}\label{sec:glossary}

\begin{description}
\item[AP] Alert Production
\item[DAC] Data Access Center
\item[DMS] Data Management System
\item[DR] Data Release.
\item[DRP] Data Release Production
\item[EPO] Education and Public Outreach
\item[MOPS] Moving Object Pipeline System
\item[SQL] Structured Query Language, the common language for querying relational databases.
\item[TBD] To Be Determined
\item[Visit] A pair of exposures of the same area of the sky taken in immediate
succession.  A Visit for LSST consists of a 15 second exposure, a 2
second readout time, and a second 15 second exposure.
\item[VO] Virtual Observatory
\item[VOEvent] A VO standard for disseminating information about transient events.
\item[WCS] World Coordinate System.  A bidirectional mapping between pixel- and sky-coordinates.
\end{description}

\clearpage

\bibliography{lsst,refs_ads,refs}

\end{document}
